BioTime

### 2019-05-20 biotime.Rmd
Deal with duplicate matches from the alternate provider matching.

Do any unmatched species have matches with other providers?
```{r}
get_match_counts(biotime_data %>% filter(is.na(id)), "matchingName")

@@

#match accepted names from 
syn_res <- by_name(na.omit(unique(alt_names$altProviderName)),"itis") %>%
                       rename(altProviderName = input) %>%
                       left_join(alt_names) %>%
  select(id = acceptedNameUsageID, input, scientificName) %>% 
  drop_na(id) %>% 
  distinct() %>%
  left_join(data %>% select(-species, -genus), by = c("input" = "genus_species"), na_matches =  "never") %>%
  rename(matchingName = input)

>>>>

Do any unmatched species have matches with other providers?
```{r}
#get_match_counts(biotime_data %>% filter(is.na(id)), "matchingName")

@@

#match accepted names from 
syn_res <- by_name(na.omit(unique(alt_names$altProviderName)),"itis") %>%
  drop_na(acceptedNameUsageID) %>% 
  rename(altProviderName = input) %>%
  left_join(alt_names, na_matches = "never")

#some names have multiple matches (same ID but multiple scinames), have to pick one
## in this case all the duplicates have an accepted and a synonym, but there are some single matches that are just synonyms
## so we have to find duplicate ID's and then filter
alt_dupes <- syn_res %>% 
  group_by(acceptedNameUsageID, input) %>%
  filter(n() > 1)

#filter duplicates for accepted, and replace old entries 
syn_res <- alt_dupes %>% 
  filter(taxonomicStatus == "accepted") %>% 
  bind_rows(syn_res %>% 
              filter(!acceptedNameUsageID %in% alt_dupes$acceptedNameUsageID)) %>%
#then finish clean up 
  select(id = acceptedNameUsageID, input, scientificName) %>% 
  distinct() %>%
  left_join(data %>% select(-species, -genus), by = c("input" = "genus_species"), na_matches =  "never") %>%
  rename(matchingName = input)
